Implementation of Set theory in \dedukti

### 2021-11-17 theoriezf/lambdapi.tex
Add files via upload

\lstdefinelanguage{Lambdapi}
{
  inputencoding=utf8,
  extendedchars=true,
  numbers=none,
  numberstyle={},
  tabsize=2,
  basicstyle={\ttfamily\upshape\mdseries},
  backgroundcolor=\color{lightgrey},
  keywords={abort,admit,admitted,apply,as,assert,assertnot,associative,assume,begin,builtin,commutative,compute,constant,debug,end,fail,flag,focus,generalize,have,in,induction,inductive,infix,injective,left,let,notation,off,on,opaque,open,prefix,print,private,proofterm,protected,prover,prover_timeout,quantifier,refine,reflexivity,require,rewrite,right,rule,sequential,simplify,solve,symbol,symmetry,type,TYPE,unif_rule,verbose,why3,with},
  sensitive=true,
  keywordstyle=\color{blue},
  morecomment=[l]{//},
  commentstyle={\itshape\color{red}},
  string=[b]{"},
  stringstyle=\color{orange},
  showstringspaces=false,
  literate=
  {↪}{$\hookrightarrow$}1
  {→}{$\rightarrow$}1
  {Π}{$\Pi$}1
  {≔}{$\coloneqq$}1
  {𝔹}{$\mathbb{B}$}1
  {𝕃}{$\mathbb{L}$}1
  {ℕ}{$\mathbb{N}$}1
  {α}{$\alpha$}1
  {π}{$\pi$}1
  {τ}{$\tau$}1
  {ω}{$\omega$}1
  {∧}{$\wedge$}1
  {≤}{$\le$}1
  {≠}{$\neq$}1
  {∉}{$\notin$}1
  {×}{$\times$}1
  {ρ}{$\rho$}1
  {∈}{$\in$}1 
}
\lstset{language={Lambdapi}}

>>>>

\lstdefinelanguage{Lambdapi}
{
  inputencoding=utf8,
  extendedchars=true,
  numbers=none,
  numberstyle={},
  tabsize=2,
  basicstyle={\ttfamily\upshape\mdseries},
  backgroundcolor=\color{lightgrey},
  keywords={abort,admit,admitted,apply,as,assert,assertnot,associative,assume,begin,builtin,commutative,compute,constant,debug,end,fail,flag,focus,generalize,have,in,induction,inductive,infix,injective,left,let,notation,off,on,opaque,open,prefix,print,private,proofterm,protected,prover,prover_timeout,quantifier,refine,reflexivity,require,rewrite,right,rule,sequential,simplify,solve,symbol,symmetry,type,TYPE,unif_rule,verbose,why3,with},
  sensitive=true,
  keywordstyle=\color{blue},
  morecomment=[l]{//},
  commentstyle={\itshape\color{red}},
  string=[b]{"},
  stringstyle=\color{orange},
  showstringspaces=false,
  literate=
  {↪}{$\hookrightarrow$}1
  {→}{$\rightarrow$}1
  {Π}{$\Pi$}1
  {≔}{$\coloneqq$}1
  {𝔹}{$\mathbb{B}$}1
  {𝕃}{$\mathbb{L}$}1
  {ℕ}{$\mathbb{N}$}1
  {α}{$\alpha$}1
  {λ}{$\lambda$}1
  {σ}{$\sigma$}1
  {π}{$\pi$}1
  {τ}{$\tau$}1
  {ω}{$\omega$}1
  {∧}{$\wedge$}1
  {∨}{$\vee$}1
  {≤}{$\le$}1
  {≠}{$\neq$}1
  {∉}{$\notin$}1
  {×}{$\times$}1
  {ρ}{$\rho$}1
  {∈}{$\in$}1
  {∀}{$\forall$}1
  {∃}{$\exists$}1
  {⇒}{$\Rightarrow$}1
  {⇔}{$\Leftrightarrow$}1
}
\lstset{language={Lambdapi}}
